---
title: "dplyr weekend homework "
output: html_notebook
---

- Library calls.

```{r}
library(tidyverse)
library(dplyr)
library(janitor)
```

- Reading in data.

```{r}
books <- read.csv("books.csv")
```

- Checking the data.

```{r}
nrow(books)
ncol(books)
--------------------------------------------------------------------------------
dim(books)
names(books)
--------------------------------------------------------------------------------
glimpse(books)
```

- Choosing which variables to keep and assigning them to 'books_info'.

```{r}
books_info <- books %>% 
 select(title:average_rating, language_code:publisher)  

#view(books_info)
```

- Checking for missing values in 'ratings' variable.

```{r}
books_info %>% 
  filter(is.na(average_rating))

--------------------------------------------------------------------------------

books_info %>% 
  summarise(count = sum(is.na(average_rating)))
```

- Changing the missing values in the 'average_ratings' for the median rating

```{r}
average_rating_imputed_median <- books_info %>%
    mutate(average_rating = coalesce(average_rating, 
                                     median(average_rating, na.rm = TRUE)))
--------------------------------------------------------------------------------
#view(average_rating_imputed_median)
```

- Which authors are the most prolific within this dataset?

```{r}
average_rating_imputed_median %>% 
  group_by(authors) %>% 
  count(authors) %>% 
  arrange(desc(n)) %>% 
  head(10)
```

- Adding logical variable for whether or not the author appears on the list for more than one book. 

```{r}
average_rating_imputed_median %>% 
  group_by(authors) %>% 
  count(authors) %>% 
  mutate(n > 1) 
```

- Authors, who are the highest rated authors? 

```{r}
average_rating_imputed_median %>%  
  group_by(authors) %>% 
  summarise(av_rating = mean(average_rating)) %>% 
  arrange(desc(av_rating)) 
```

```{r}
average_rating_imputed_median %>%  
  group_by(authors) %>% 
  summarise(av_rating = mean(average_rating)) %>%
  arrange(desc(av_rating)) %>% 
  filter(av_rating == 5)
```
* There are 18 authors who all have an average rating of 5.

- Who are the lowest rated authors?

```{r}
average_rating_imputed_median %>%  
  group_by(authors) %>% 
  summarise(av_rating = mean(average_rating)) %>% 
  arrange(av_rating) 
```

* I have done something wrong with the imputing missing values with median, not sure what sorry! Going to try and remove titles which do not have a rating instead.

- Assigning the data back to 'books_info' as i couldn't get 'average_rating_imputed_median' to work as desired.

```{r}
books_info <- average_rating_imputed_median
```

- Trying to idetity the type of variable 'average_rating' is in order to change it to 'character' so I can change it to 'character'. I want to do this as I am trying to replace all '0.000' ratings with 'NA' in order to use `drop_na()`. This would allow me to have a fairer representation of the lowest rated authors.

```{r}
books_info %>% 
class(av_rating)

books_info %>% 
mutate('av_rating' = as.character('av_rating'))

--------------------------------------------------------------------------------

 books_info %>% 
  mutate(av_rating = na_if(av_rating, "0.000")) 
  
# I can't get this to work, going to try filter the 0s out instead.  
```


```{r}
ratings_above_zero <- books_info %>% 
  filter(average_rating > 0) 
--------------------------------------------------------------------------------
#view(ratings_above_zero)
```

```{r}
ratings_above_zero %>% 
  arrange(average_rating)

--------------------------------------------------------------------------------
  
ratings_above_zero %>%  
  group_by(authors) %>% 
  summarise(av_rating = mean(average_rating)) %>% 
  arrange(av_rating) %>% 
  slice_max(av_rating, n = 10)
```


- I am now going to try and find out what is the average rating for all books and which book is the most reviewed on the list.

```{r}
books_info %>% 
  summarise(overall_average_rating = mean(average_rating)) %>% 
  pull()
```

- Next I would like to see the most rated book

```{r}
 books_info %>% 
  arrange(desc(ratings_count)) %>% 
  slice_head()
```
- I would also like to see which book has been reviewed with text the most often

```{r}
books_info %>% 
  arrange(desc(text_reviews_count)) %>% 
  slice_head()
```
* Both the same book.

- Next I would like to see which publisher has the most books on the list and which publisher has the highest overall 'average_rating'

```{r}
by_publisher <- books_info %>% 
  group_by(publisher) 

view(by_publisher)
```


```{r}
by_publisher %>% 
  count(publisher) %>% 
  arrange(desc(n)) %>% 
  head(10) 
```

```{r}
by_publisher %>% 
  group_by(publisher) %>% 
  summarise(pub_av_rating = mean(average_rating)) %>% 
  arrange(desc(pub_av_rating)) 
```

