---
title: "Cleaning&ExtraDplyrHomeworkCaitlinDonaghy"
output: html_document
date: "2023-03-22"
---

```{r}
library(tidyverse)

library(janitor)
```

```{r}
movies <- read_csv("movies.csv")
view(movies)
```

# Question 1.

I would start by viewing the dataset to familiarise myself with it. I would then begin identifying and removing any metadata then use the `janitor()` function to clean names. i would then find and address any missing values using `filter()` along with `is.na`, I would remove them with `drop_na()` or impute them with `coalesce()` and `na.rm = TRUE` with meaningful values i.e `mean()` or `median()`. Or I would relable them as missing and ignore or work around them.

# Question 2.

```{r}

movies_selected <- select(movies, title, runtime, budget)
view(movies_selected)
```

# Question 3.

```{r}
movies_selected %>% 
  summarise(count = sum(is.na(title)))
```
```{r}
movies_selected %>% 
  summarise(count = sum(is.na(runtime)))
```
```{r}
movies_selected %>% 
  summarise(count = sum(is.na(budget)))
```
or 

```{r}
movies_selected %>% 
  summarise(count = sum(is.na(movies_selected)))
```


# Question 4.

```{r}
movies_imputed <- movies_selected %>% 
  mutate(runtime = coalesce(runtime, mean(runtime, na.rm = TRUE))) %>% 
  view(movies_imputed)

```

I'm not sure I have done that correctly, there are no missing values (NA) but 35 of the movies have a runtime of 0 which seems like a missing value.

# Question 5.

```{r}
movies_imputed %>% slice_min(runtime, n = 10)
```
```{r}
movies_imputed %>% slice_max(runtime, n = 10)
```

Question 7.
Using the if_else function, impute anything with a budget below $100 with the median budget. Overwrite your movies_imputed so it contains the new budget values.
```{r}
movies_imputed %>% 
median_budget <- median(budget)

median_budget <- movies_imputed %>%
    mutate(budget = coalesce(budget, median(budget, n < 100)))
```


```{r}
movies_imputed %>% 
  select(budget) %>% 
  median(budget = if_else(budget < 100) 
                                )

```
```{r}
movies_imputed  %>% 
  select(budget) %>% 
  mutate(budget = if_else(budget < "100")
  )
```

Sorry about all the rubbish above, I can't work out Q7 and it's 21:00 so I'm calling it a night!