---
title: "Tidyverse_consolidation_homework"
output: html_document
date: "`r Sys.Date()`"
---

```{r}
library(tidyverse)
library(dplyr)
```
Q1. Load the code_clan_tweets.csv data. Find the number of rows, columns, and list all the variable names.

```{r}
cc_info <- read_csv("code_clan_info.csv")

cc_tweets <- read_csv("code_clan_tweets.csv")


```
```{r}
glimpse(cc_info)
```
```{r}
glimpse(cc_tweets)
```
Q2. Find the total number of favourites (stored in favorite_count) that CodeClan tweets have got. Don’t add a tweet’s favorite_count to the total when the tweet was quoted (see the is_quote variable).

```{r}

cc_tweets %>% 
  mutate(favorite_count_total = sum(favorite_count, na.rm = TRUE),
         .after = favorite_count)

```
I'm sorry, I know the quote tweets weren't omitted, I just can't seem to work it out tonight. 

Q3. Summarise the mean number of retweets (retweet_count), split by the type of platform that was used to tweet (source). Again, omit quoted tweets from the mean.

```{r}

cc_tweets %>% 
  mutate(retweet_count = as.numeric(retweet_count))

cc_tweets %>% 
  mean(retweet_count, na.rm = TRUE)

#mean(results $ retweet_count, na.rm = TRUE)



```

Q4. Count the total number of likes (i.e. total of favorite_count), split by media type, and arrange them from most likes to least. Assume that any tweets without a listed media type are of type “text”.

```{r}
cc_tweets %>% 
  sum(favorite_count, na.rm = TRUE) %>% 
  split(favourite_count, media_type)
                      
```

Q5. Find the mean number of characters that a CodeClan tweet contains. You can either find a way to count the text in the text variable, or use the variable display_text_width which contains a count. Checking both would be a good idea if possible to see if they match (but it’s not essential).

```{r}

```

Q6. The code_clan_info.csv data file contains status_url along with other info. Load this in, and join it to the code_clan_tweets tibble, so that you have a status_url for each tweet. Decide which variable to join the tibbles on.

```{r}
tweet_tibble <- full_join(cc_info, cc_tweets, by = "tweet_id")

tweet_tibble
```

Q7.From your new joined data, create a new tibble codeclan_hashtags containing only tweet_id and hashtags, then convert hashtags into lowercase for analysis. Keep only those tweets with hashtags.

```{r}
codeclan_hashtags <- tweet_tibble %>% 
  select(tweet_id, hashtags)

codeclan_hashtags %>% 
  str_to_lower(hashtags)
```

